Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-09 Paper/paper.tex
Citation normalization

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others. \cite{EvolutionOfWeb} In that same time period, the number of global internet users has grown to somewhere around two and a half billion. \cite{EvolutionOfWeb} The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on. \cite{ErrorsInTheWild} That may seem like a incredibly small amount for such monoliths but every error is an opportunity for malfunction and customer dissatisfaction.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox back in 2009. \cite{EvolutionOfWeb} HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014. \cite{Plan2014} What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

@@

\subsection{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation application. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

Node is found in a number of popular sites including: PayPal, The New York Times, Yahoo!, Uber, LinkedIn, Microsoft Azure, and a number of others. \cite{Node}

@@

\section{Defining Testing}
IEEE defines software testing as ``the dynamic verification of the behavior of a program on a finite set of test cases, suitably selected from the usually infinite executions domain, against the expected behavior.'' \cite{TestingDefinition} Put a bit more simply, software testing is the process of making sure the program does what it is supposed to.

@@

\subsection{Testing Statistics}
It is widely accepted that the earlier a developer detects a defect, the easier it is to fix that defect. A famous book, ``Code Complete'' by Steve McConnell \cite{DefectPic}, includes the following figure, showing this statistic on a rough graph.

@@

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB.\cite{ToDoAppHomePage} Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, marking tasks as completed, and viewing completed tasks. Here is a brief preview of the application's UI:

@@

The default Jasmine did not support Node.js but there was a package available through npm called jasmine-node \cite{JasmineNode} that gave jasmine access to the node package and functions.

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because that is what Node.JS uses, which is used by our evaluation applications.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

Nightwatch, as of this writing, has the ability to open Firefox, Chrome, and Internet Explorer. As of February 2014, Chrome is used by 46.69\% of internet users, Internet Explorer is used by 24.39\% and Firefox is used by 20.78\%.\cite{BrowserStats} Together that accounts for 91.86\% of all internet users.

@@

Developers like ZombieJS syntax so much that there exists a wrapper that uses ZombieJS's API around PhantomJS. \cite{ZombiePhantom}

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is an offline Continuous Integration tool, the only offline tool that we found with active developement and support. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

@@

In order to get access to private repositories, Travis offers several pricing plans, the cheapest of which is \$129 \cite{TravisPricing} for their ``Startup'' plan. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

@@

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and JavaScript and as of February 26th they now offer official support for Clojure projects.\cite{SemaphoreBlog} These types of projects require no setup or files in the repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are discussed in their developer guide. \cite{NightwatchJS}

\subsection{Setting up Istanbul}
As mentioned in the Istanbul section, getting it running is simple. Install Istanbul with npm: \lstinline{npm install -g istanbul} and then run the istanbul command along with any others needed. In our case, we ran \lstinline{istanbul cover mocha -- . -R spec} to run Istanbul on our Mocha unit tests. For a more detailed view of possible commands and arguments, the developer can check out the Istanbul page. \cite{Istanbul}

\subsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a JavaScript file named ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''. \cite{GruntJS}

>>>>

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others\cite{EvolutionOfWeb}. In that same time period, the number of global internet users has grown to somewhere around two and a half billion\cite{EvolutionOfWeb}. The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on\cite{ErrorsInTheWild}. That may seem like a incredibly small amount for such monoliths but every error is an opportunity for malfunction and customer dissatisfaction.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators\cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox back in 2009\cite{EvolutionOfWeb}. HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014\cite{Plan2014}. What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

@@

\subsection{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation application. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.''\cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

Node is found in a number of popular sites including: PayPal, The New York Times, Yahoo!, Uber, LinkedIn, Microsoft Azure, and a number of others\cite{Node}.

@@

\section{Defining Testing}
IEEE defines software testing as ``the dynamic verification of the behavior of a program on a finite set of test cases, suitably selected from the usually infinite executions domain, against the expected behavior.''\cite{TestingDefinition} Put a bit more simply, software testing is the process of making sure the program does what it is supposed to.

@@

\subsection{Testing Statistics}
It is widely accepted that the earlier a developer detects a defect, the easier it is to fix that defect. A famous book, ``Code Complete'' by Steve McConnell\cite{DefectPic}, includes the following figure, showing this statistic on a rough graph.

@@

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB\cite{ToDoAppHomePage}. Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, marking tasks as completed, and viewing completed tasks. Here is a brief preview of the application's UI:

@@

The default Jasmine did not support Node.js but there was a package available through npm called jasmine-node\cite{JasmineNode} that gave jasmine access to the node package and functions.

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas\cite{AMDInfo}. Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because that is what Node.JS uses, which is used by our evaluation applications.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran\cite{Istanbul}.

@@

Nightwatch, as of this writing, has the ability to open Firefox, Chrome, and Internet Explorer. As of February 2014, Chrome is used by 46.69\% of internet users, Internet Explorer is used by 24.39\% and Firefox is used by 20.78\%\cite{BrowserStats}. Together that accounts for 91.86\% of all internet users.

@@

Developers like ZombieJS syntax so much that there exists a wrapper that uses ZombieJS's API around PhantomJS\cite{ZombiePhantom}.

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is an offline Continuous Integration tool, the only offline tool that we found with active developement and support. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members\cite{JenkinsGitHub}. Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

@@

In order to get access to private repositories, Travis offers several pricing plans, the cheapest of which is \$129\cite{TravisPricing} for their ``Startup'' plan. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

@@

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and JavaScript and as of February 26th they now offer official support for Clojure projects\cite{SemaphoreBlog}. These types of projects require no setup or files in the repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are discussed in their developer guide\cite{NightwatchJS}.

\subsection{Setting up Istanbul}
As mentioned in the Istanbul section, getting it running is simple. Install Istanbul with npm: \lstinline{npm install -g istanbul} and then run the istanbul command along with any others needed. In our case, we ran \lstinline{istanbul cover mocha -- . -R spec} to run Istanbul on our Mocha unit tests. For a more detailed view of possible commands and arguments, the developer can check out the Istanbul page\cite{Istanbul}.

\subsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a JavaScript file named ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''\cite{GruntJS}.
